FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-02-05 ess_marmo.tex
Renaming files.

\subsubsection{FITS to PDS3 and PDS4 dictionaries}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% A: Here Is Appendix Title
%
\appendix
\section{Correspondence between reserved FITS keywords and PDS4 standard reference}
\label{app:stdfitspds4}
%This is an Appendix section.
The correspondence between mandatory and reserved FITS keywords (as defined in
the last version of the FITS standard document\footnote{https://fits.gsfc.nasa.gov/standard40/fits\_standard40aa.pdf})
and PDS4 attributes, is described in this Appendix.
\begin{itemize}
\item{\texttt{BITPIX}.
It specifies the number of bits that represent a data value in
the associated data array.
PDS4 uses the attribute \texttt{data\_type}: correspondent 
values depend on the associated object class.}

\item{\texttt{BLANK}.
This keyword must be used only in integer data.
It contains an integer that specifies the value that is used to
represent pixels that have an undefined physical value.}

\item{\texttt{DATAMAX}}
\item{\texttt{DATAMIN}}
\item{\texttt{DATE}}
\item{\texttt{DATE-OBS}}
\item{\texttt{INSTRUME}}
\item{\texttt{TELESCOP}}
\item{\texttt{OBJECT}}
\item{\texttt{ORIGIN}}
\item{\texttt{AUTHOR}}
\item{\texttt{REFERENC}}

>>>>

\subsubsection{Correspondence between reserved FITS keywords and PDS4 standard reference}
\label{sssec:stdfitspds4}
The correspondence between mandatory and reserved FITS keywords (as defined in
the last version of the FITS standard document\footnote{https://fits.gsfc.nasa.gov/standard40/fits\_standard40aa.pdf})
and PDS4 attributes, is described here.
\begin{itemize}
\item{\texttt{BITPIX}.
It specifies the number of bits that represent a data value in
the associated data array.
PDS4 uses the attribute \texttt{data\_type}: correspondent 
values depend on the associated object class.}

\item{\texttt{BLANK}.
This keyword must be used only in integer data.
It contains an integer that specifies the value that is used to
represent pixels that have an undefined physical value.... 
\textit{PDS4 Special\_Constants?}}

\item{\texttt{DATAMAX}}
\item{\texttt{DATAMIN}}

\item{\texttt{DATE}.
The date on which the file was created,}
\item{\texttt{DATE-OBS}}
\item{\texttt{INSTRUME}}
\item{\texttt{TELESCOP}}
\item{\texttt{OBJECT}}
\item{\texttt{ORIGIN}}
\item{\texttt{AUTHOR}}
\item{\texttt{REFERENC}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% A: Here Is Appendix Title
%
%\appendix
%\section{Here Is Appendix Title}
%This is an Appendix section.
